---
title: "Final Project Proposal"
date: "14/11/2019"
output: html_document
---

# STAT 240 Final Project Proposal (Group: 313:2)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Group Number 313:2

## Members Present

- Charles Saunders
- Kelli Unruh
- Adam Bauer
- Krishna Jangid


## Questions that motivate the study:

- The top trending channels in each country
- Most trending category over the year.
- The relation between comments, categories, and likes.
- Do more dislikes can also trend videos?
- If there are comments disabled do people still like those videos.
- Over years we can predict the grown of a particular channel through their trending video timelines.
- Does a particular time of year also have particular tags?
- For trending videos do they have any patterns in tags?
- Over different countries can we predict common interests.
- Patterns in the name for trending videos.


## Data preview

We have data for 8 countries ( USA, Great Britain, Canada, France, Russia, Mexico, Japan, and India) about top trending videos over 205 days in CSV and we have categories id referenced in JSON. There are 16 columns:

- video_id: contains a unique id of the video (string)
- trending_date: the date when this video was trending. (date)
- title: title of that video (string)
- channel_title: the channel name from where it was published (string)
- category_id: id of category reference from JSON (number)
- publish_time: time video was published (date)
- tags: tags for the video (string)
- views: # of views on that video (number)
- likes: # of likes on that video (number)
- dislikes: # of dislikes on that video (number)
- comment_count: #of comments on that video (number)
- thumbnail_link: thumbnail link of that video (string)
- comments_disabled: are comments disabled on that video (bool)
- ratings_disabled: are ratings disabled on that video (bool)
- video_error_or_removed: is videos removed or there is an error (bool)
- description: description of that videos (string) 

Here is a how US data looks like.

```{r read_data}
us = read.csv("USvideos.csv")
head(us)
```

## Methods 

- We are going to use readr/lubridate/tidyr to clean and restructure data.
- For predicting the growth of channels we are going to use statistical models.


